---
title: "SCRPS For Different Distributions"
output: html_document
date: '2022-06-08'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# SCRPS for Normal distribution 
Implementation using the following expression:   
$\text{SCRPS}(\text{N}(\mu, \sigma^2),y) = -\sqrt\pi \phi(z) - \frac{\sqrt\pi z}{2}(2\Phi(z)-1) - \frac{1}{2} \log(\frac{2\sigma}{\sqrt\pi})\\ \text{wheer} \ z = \frac{\mu - y}{\sigma} \  \text{and} \  \phi, \Phi \text{are, respectively,  the  density function and the cumulative distribution function of the standard normal distribution.}$


```{r}

SCRPS_norm <- function(y, mean = 0, sd = 1) {
  z <- (mean-y) /sd
  score <- -sqrt(pi)*dnorm(z) - sqrt(pi)*z/2 * (2*pnorm(z) - 1) - 0.5*log(2*s/sqrt(pi))
  
  return(score)
}


```
test

```{r} 
n <- 100000
k <- 50
count <- 0
for (i in 1:k) {
  y1 <- runif(1, min = -1000, max = 1000)
  m <- runif(1, min = -100, max = 100)
  s  <- runif(1, min = 1, max = 50)
 
   score1 <- SCRPS_norm(y1,mean = m, sd = s)
   sample1 <- rnorm(n,mean = m, sd = s)
   E1 <- mean(abs(sample1 - y1))
   sample1 <- rnorm(n,mean = m, sd = s)
   sample2 <- rnorm(n,mean = m, sd = s)
   E2 <- mean(abs(sample1 - sample2))
   score2 <- -E1/E2 - 0.5*log(E2)
   
   if (abs(score1 - score2) < 0.1) {
     count <- count + 1
   } else {
     print(score1)
     print(score2)
     print("______")
   }

}


print(count/k)

```
# SCRPS for exponential distribution 

Implementation using the following expression:   
$\text{SCRPS}(\text{Exp}(\lambda),y) = -\frac{E_1}{E_2} - \frac{1}{2}\log(E_2)$  

where 

$$ E_1 =   \left\{
\begin{array}{ll}
      \frac{1}{\lambda} - y & y <= 0 \\
      \frac{2}{\lambda}e^{-\lambda y} + y -\frac1{\lambda} & 0 < y \\
\end{array} 
\right.  $$

and 

$E_2 = \frac{1}{\lambda}$

```{r}
SCRPS_exp <- function(y, l = 1){
  if (y <= 0) {
    E1 <- 1/l - y
  } else {
    E1 <- (2*exp(-l*y))/l + y - 1/l
  }
  E2 <- 1/l
  score <- -E1/E2 - 0.5*log(E2)
  return(score)
}

```




test

```{r} 

n <- 100000
k <- 50
count <- 0
for (i in 1:k) {
  y1 <- runif(1, min = -1000, max = 1000)
  l1 <- runif(1, min = 1, max = 10)
 
  score1 <- SCRPS_exp(y1,l=l1)
  sample1 <- rexp(n,rate=l1)
  E1 <- mean(abs(sample1 - y1))
  sample1 <- rexp(n,rate=l1)
  sample2 <- rexp(n,rate=l1)
  E2 <- mean(abs(sample1 - sample2))
  score2 <- -E1/E2 - 0.5*log(E2)
   
   if (abs(score1 - score2) < 5) {
     count <- count + 1
   } else {
     print(score1)
     print(score2)
     print("______")
   }

}


print(count/k)

```





# SCRPS for uniform distribution 

Implementation using the following expression:

$\text{SCRPS}(\text{unif}(a, b),y) = -\frac{E_1}{E_2} - \frac{1}{2}\log(E_2)$  

where 
$$ E_1 =   \left\{
\begin{array}{ll}
      \frac{b+a}{2} - y & y <= a \\
      \frac{y(y-b-a) + \frac{a^2 + b^2}{2}}{b-a} & a < y < b \\
      y - \frac{b+a}{2} & b <= y \\
\end{array} 
\right.  $$

and 

$E_2 = \frac{b-a}{3}$

```{r}
SCRPS_unif <- function(y, min = 0, max = 1){
  if (y <= min) {
    E1 <- 0.5*(min + max) - y
  } else if (y >= max) {
    E1 <- y - 0.5*(min + max)
  } else {
    E1 <- (y*(y-min-max)+0.5*(min^2 + max^2))/(max-min)
  }
 
  E2 <- (max - min)/(3)
  score <- -E1/E2 -0.5*log(E2)
  return(score)
}

```




test

```{r} 
n <- 100000
k <- 50
count <- 0
for (i in 1:k) {
  y1 <- runif(1, min = -1000, max = 1000)
  a <- runif(1, min = -100, max = 100)
  b <- runif(1, min = a + 1, max = 150)
  score1 <- SCRPS_unif(y1,min = a, max = b)
  sample1 <- runif(n,min = a, max = b)
  E1 <- mean(abs(sample1 - y1))
  sample1 <- runif(n,min = a, max = b)
  sample2 <- runif(n,min = a, max = b)
  E2 <- mean(abs(sample1 - sample2))
  score2 <- -E1/E2 - 0.5*log(E2)
   
   if (abs(score1 - score2) < 0.1) {
     count <- count + 1
   } else {
     print(score1)
     print(score2)
     print("______")
   }

}


print(count/k)
```




# SCRPS for exponential distribution with flexible location and scale

Implementation using the following expression:   
$\text{SCRPS}(\text{Exp}(\lambda,\text{location } a, \text{scale } b),y) = -\frac{E_1}{E_2} - \frac{1}{2}\log(E_2)$  

where 

$$ E_1 =   \left\{
\begin{array}{ll}
      a + \frac{b}{\lambda} - y & y <= a \\
      \frac{b}{\lambda}(2e^{-\lambda (\frac{y-a}{b})} - 1) + y -a & a < y \\
\end{array} 
\right.  $$

and 

$E_2 = \frac{b}{\lambda}$

```{r}
SCRPS_exp2 <- function(y, l = 1, a = 0, b = 1){
  if (y <= a) {
    E1 <- a + b/l - y
  } else {
    E1 <- (b/l)*(2*exp(-l*((y-a)/b)) - 1) + y - a
  }
  E2 <- b/l
  score <- -E1/E2 - 0.5*log(E2)
  return(score)
}

```




test

```{r} 
n <- 100000
k <- 50
count <- 0
for (i in 1:k) {
  y1 <- runif(1, min = -1000, max = 1000)
  l1 <- runif(1, min = 1, max = 10)
  a1 <- runif(1, min = -100, max = 100)
  b1 <- runif(1, min = 1, max = 50)
  
  score1 <- SCRPS_exp2(y1,l=l1, a = a1, b = b1)
  sample1 <- rexp(n,rate=l1)
  sample1 <- a1 + b1*sample1
  E1 <- mean(abs(sample1 - y1))
  sample1 <- rexp(n,rate=l1)
  sample1 <- a1 + b1*sample1
  sample2 <- rexp(n,rate=l1)
  sample2 <- a1 + b1*sample2
  E2 <- mean(abs(sample1 - sample2))
  score2 <- -E1/E2 - 0.5*log(E2)

   
   if (abs(score1 - score2) < 1) {
     count <- count + 1
   } else {
     print(score1)
     print(score2)
     print("______")
   }

}


print(count/k)
```


